PhD Defense

### 2023-05-31 presentation/phd_defense_pres.tex
Add Intuition and Kolmogorov slides for CS

\begin{frame}{Results: Burger's Equation}
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}
\end{frame}

\begin{frame}{Results: Burger's Equation}
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}

	When we capture 2 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_2.pdf}
\end{frame}

\begin{frame}{Results: Burger's Equation}
	Aggregated results
\end{frame}

\begin{frame}{Results: Interpretation}

@@

\begin{frame}{Results: Kolmogorov Flow OR Real Example}
\end{frame}

\begin{frame}{Conclusion}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

>>>>

\begin{frame}{Results: Burger's Equation}
	\uncover<1->{
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}
	}
	\uncover<2->{
	When we capture 2 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_2.pdf}
	}

@@

\begin{frame}{Results: Burger's Equation}
	\includegraphics[width=\textwidth]{Figures/cs_burgers_psnr.png}
\end{frame}

\begin{frame}[label=again]{Results: Kolmogorov Flow}
	\animategraphics[loop,width=\textwidth]{5}{Figures/kolm_example_anim_}{0}{19}
\end{frame}

\begin{frame}{Results: Kolmogorov Flow}
	\includegraphics[width=\textwidth]{Figures/cs_kolm_aggregate.png}
\end{frame}

\begin{frame}{Results: Interpretation}
	\only<1>{\includegraphics[width=\textwidth]{Figures/cs_int_1.png}}
	\only<2>{\includegraphics[width=\textwidth]{Figures/cs_int_2.png}}
	\only<3>{\includegraphics[width=\textwidth]{Figures/cs_int_3.png}}
\end{frame}

\againframe{again}

\begin{frame}{Results: Interpretation}
	\only<1>{\includegraphics[width=\textwidth]{Figures/cs_int_3.png}}
	\only<2>{\includegraphics[width=\textwidth]{Figures/cs_int_4.png}}
	\only<3>{\includegraphics[width=\textwidth]{Figures/cs_int_5.png}}
\end{frame}

\againframe{again}

\begin{frame}{Results: Interpretation}
	\only<1>{\includegraphics[width=\textwidth]{Figures/cs_int_5.png}}
	\only<2>{\includegraphics[width=\textwidth]{Figures/cs_int_6.png}}
	\only<3>{\includegraphics[width=\textwidth]{Figures/cs_int_7.png}}
\end{frame}

\againframe{again}

\begin{frame}{Results: Gas Monitoring}

\begin{frame}{Conclusion and Acknowledgments}
